|

### 2023-03-12 paper/00-main.Rmd
added unsuccess pass rush play

authors: 
- name: Quang Nguyen
  thanks: Corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Loyola University Chicago

@@

abstract: |
  The text of your abstract.  200 or fewer words.

bibliography: bibliography.bib
output: rticles::asa_article
---

>>>>

authors: 
- name: Quang Nguyen
  thanks: Corresponding author's email
  affiliation: Department of Statistics & Data Science, Carnegie Mellon University
- name: Ronald Yurko
  affiliation: Department of Statistics & Data Science, Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: Department of Mathematics and Statistics, Loyola University Chicago

@@

# abstract from BDB submission form
# rewrite this
abstract: |
  This paper evaluates pass rusher performance in the National Football League. We propose STRAIN, a new measure for pass rusher effectiveness, which accounts for the distance between the pass rusher and quarterback and the rate at which this distance is being reduced. STRAIN is a simple and interpretable statistic, with higher STRAIN corresponds to greater pass rushing ability. Our metric is closely related to the concept of "strain rate" in materials science. We present the mathematical motivations for our metric, followed by an illustration with an example play. The analysis concludes with a comparison of STRAIN for different positions and our rankings of NFL's best pass-rushers according to our metric.

bibliography: bibliography.bib
output: rticles::asa_article
header-includes:
  \renewcommand{\arraystretch}{0.9}
---

### 2023-03-12 paper/02-methods.Rmd
added unsuccess pass rush play

According, the **strain rate** of a material measures the change in its deformation with respect to time.
Mathematically, the strain rate of a material can be expressed as the derivative of its strain.
That is,
\begin{equation}
s'(t) = \frac{ds}{dt} = \frac{v(t)}{L_{0}},
\end{equation}
where $v(t)$ is the velocity at which the two points of interest within the material are moving away from or towards each other.
Whereas strain has no units, the strain rate is measured in inverse of time, usually 1/second.

@@

Since we only observe the distance and velocity quantities discretely in increments of 10 frames/second, a point estimate for our proposed metric STRAIN for pass rusher $j$ at frame $t$ during play $i$ is 
\begin{equation}
\widehat{\text{STRAIN}}_{ij}(t) = \cfrac{-\cfrac{f_{d_{ij}}(t) - f_{d_{ij}}(t - 1)}{0.1}}{f_{d_{ij}}(t)}.
\end{equation}
Notice that this quantity increases in two ways: 1) the rate at which the rusher is moving towards the quarterback increases, and 2) the distance between the rusher and the quarterback gets smaller.
Both of these are indications of pass rusher effectiveness.
Finally, our statistic STRAIN is measured in inverse second, similar to strain rate.
In addition, the reciprocal of our metric (1/STRAIN) has a straightforward interpretation.
It illustrates the amount of time required for the rusher to get to the quarterback at the current location and rate at any given time $t$.

>>>>

Accordingly, the **strain rate** of a material measures the change in its deformation with respect to time.
Mathematically, the strain rate of a material can be expressed as the derivative of its strain.
That is,
\begin{equation}
s'(t) = \frac{ds}{dt} = \frac{v(t)}{L_{0}},
\end{equation}
where $v(t)$ is the velocity at which the two points of interest within the material are moving away from or towards each other.
Whereas strain has no units, the strain rate is measured in inverse of time, usually 1/second.

@@

Since we only observe the distance and velocity quantities discretely in increments of 10 frames/second, a point estimate for our proposed metric STRAIN for pass rusher $j$ at frame $t$ during play $i$ is 
\begin{equation}
\widehat{\text{STRAIN}}_{ij}(t) = \cfrac{-\cfrac{f_{d_{ij}}(t) - f_{d_{ij}}(t - 1)}{0.1}}{f_{d_{ij}}(t)}.
\end{equation}
Notice that this quantity increases in two ways: 1) the rate at which the rusher is moving towards the quarterback increases, and 2) the distance between the rusher and the quarterback gets smaller.
Both of these are indications of an effective pass rush attempt.
Finally, our statistic STRAIN is measured in inverse second, similar to strain rate.
In addition, the reciprocal of our metric (1/STRAIN) has a straightforward interpretation:
it illustrates the amount of time required for the rusher to get to the quarterback at the current location and rate at any given time $t$.

### 2023-03-12 paper/03-results.Rmd
added unsuccess pass rush play

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "01_fig_field.R"))
fig_field
```

@@

```{r}
#| label: fig_crosby_curves
#| fig.cap: "crosby"
#| fig.width: 5
#| fig.height: 3
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

\ref{tab:edge}

\ref{tab:interior}

>>>>

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 6.6
#| fig.height: 4.4
source(here("scripts", "01_fig_field.R"))
fig_field
```

@@

```{r}
#| label: fig_crosby_curves
#| fig.cap: "crosby"
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

Table \ref{tab:edge}

Table \ref{tab:interior}
